Translation Elicitation: laboratory notes

### 2022-11-14 index.qmd
Update lab notes

---
title: "Translation Elicitation: laboratory notes"
date: "Last updated: `r format(Sys.Date(), '%d/%m/%Y')`"
format:
    html:
        toc: true
        number-sections: true
        bibliography: "references.bib"
        csl: "apa7.csl"
        warnings: false
        messages: false
        fig-dpi: 600
        out-width: "80%"
        code-fold: true
---

```{r}
#| label: setup
#| include: false
my_colours <- c("#1A85FF", "#ff2976", "#FFC20A")

@@

```{r}
#| label: tbl-stimuli
tab_subtitle <- md("Lexical frequency, phonological neigbourhood size, and levenshtein distance of the stimuli words.")

tab_note <- md("*Note*. Median and standard deviation (*SD*) of lexical frequencies of target words (expressed in counts per million and as Zipf scores), density of higher-frequency phonological neighbourhoods of target words, and normalised Levenshtein phonological similarity between the presented and the target words.")

stimuli %>% 
    select(group, word_1, freq_2, freq_zipf_2, nd, lv) %>% 
    group_by(group) %>% 
    summarise(
        across(
            freq_2:lv, 
            list(
                median = ~median(., na.rm = TRUE),
                sd = ~sd(., na.rm = TRUE)
            )
        )
    ) %>%
    gt(rowname_col = "group") %>% 
    tab_header(title = md("Table 1"), subtitle = tab_subtitle) %>% 
    tab_source_note(tab_note) %>% 
    fmt_number(freq_2_median:nd_sd) %>%
    fmt_percent(matches("lv|global")) %>% 
    tab_spanner(
        md("**Freq. (million)**"),
        c("freq_2_median", "freq_2_sd", "freq_zipf_2_median", "freq_zipf_2_sd")
    ) %>% 
    tab_spanner(md("**Freq. (Zipf)**"), matches("freq_zipf_2")) %>% 
    tab_spanner(md("**Neighbours**"), matches("nd")) %>% 
    tab_spanner(md("**Levenshtein**"), matches("lv")) %>% 
    cols_label(
        freq_2_median = md("Median"),
        freq_2_sd = md("*SD*"),
        freq_zipf_2_median = md("Median"),
        freq_zipf_2_sd = md("*SD*"),
        nd_median = md("Median"),
        nd_sd = md("*SD*"),
        lv_median = md("Median"),
        lv_sd = md("*SD*")
    ) %>% 
    summary_rows(
        columns = c(matches("median"), -matches("lv")),
        fns = list(Median = "median", SD = "sd")
    ) %>% 
    summary_rows(
        columns = matches("lv"),
        fns = list(Median = "median", SD = "sd"), 
        formatter = fmt_percent
    ) %>% 
    tab_style(
        style = cell_text(align = "left", weight = "bold", size = "medium"),
        locations = cells_title(groups = "title")
    ) %>% 
    tab_style(
        style = cell_text(align = "left", size = "medium", style = "italic"),
        locations = cells_title(groups = "subtitle")
    ) %>% 
    tab_style(
        style = cell_text(align = "left", size = "medium"),
        locations = cells_source_notes()
    ) %>% 
    tab_style(
        style = cell_text(align = "left", size = "medium"),
        locations = cells_stub_grand_summary()
    ) %>% 
    tab_style(
        style = cell_borders(sides = c("left", "right"), color = "white"),
        locations = list(
            cells_body(),
            cells_row_groups(),
            cells_column_spanners(), 
            cells_stub(),
            cells_stub_grand_summary(), 
            cells_source_notes(),
            cells_column_labels(),
            cells_stubhead()
        )
    ) %>% 
    tab_style(
        style = list(
            cell_text(align = "left", size = "medium"),
            cell_borders(sides = "all", color = "white")
        ),
        locations = cells_stub()
    ) %>% 
    tab_style(
        style = cell_text(
            align = "center", 
            size = "medium",
            weight = "normal",
            style = "normal"
        ),
        locations = list(
            cells_column_spanners(),
            cells_column_labels()
        )
    ) %>% 
    tab_style(
        style = cell_borders(sides = "all", color = "white"),
        locations = cells_body(columns = 1:9)
    ) %>% 
    tab_style(
        style = cell_borders(sides = "top", color = "white"),
        locations = cells_body(columns = 1:9)
    )
```

@@

```{r}
#| label: fig-stimuli-pthn
#| fig-height: 10
stimuli %>% 
    left_join(count(., group, name = "n_total")) %>% 
    mutate(translation = paste0(word_1, "/", word_2)) %>% 
    ggplot(aes(x = nd, y = reorder(translation, nd), colour = group, fill = group, label = translation)) +
    facet_wrap(~group, scales = "free_y") +
    geom_text(size = 3, hjust = 0) +
    labs(
        x = "Group", 
        y = "# phonological neighbours", 
    ) +
    scale_x_continuous(breaks = seq(0, 30, 5)) +
    theme(
        legend.position = "none",
        panel.grid.major.x = element_line(colour = "grey", linetype = "dotted"),
        axis.ticks.y = element_blank(),
        axis.text.y = element_blank()
    )
```

@@

```{r}
#| label: fig-stimuli-lv
#| fig-width: 9
#| fig-height: 12
stimuli %>% 
    left_join(count(., group, name = "n_total")) %>% 
    mutate(group = paste0(group,  " (N = ", n_total, ")")) %>% 
    ggplot() +
    aes(x = lv, y = reorder_within(translation, lv, group), fill = group, colour = group) +
    facet_wrap(~group, scales = "free_y") +
    geom_text(aes(label = percent(lv, accuracy = 0.1)), size = 3, hjust = 0) +
    labs(
        x = "Group", 
        y = "Phonological Leveshtein distance\n(corrected for string length)",
        fill = "Test language"
    ) +
    scale_x_continuous(labels = percent) +
    scale_y_reordered() +
    theme(
        legend.position = "none",
        axis.title.y = element_blank(),
        axis.text.y = element_text(size = 7, hjust = 1),
        panel.grid.major.x = element_line(colour = "grey", linetype = "dotted")
    ) 
ggsave(here("img", "lv.png"), height = 12)
```

@@

    # PTHN 1
    stimuli %>% 
    count(group, nd) %>% 
    ggplot(aes(x = nd, y = n, fill = group)) + 
    facet_wrap(~group, ncol = 1) + 
    geom_rect(
        data = medians, 
        aes(xmin = 0, xmax = nd_median+nd_sd, ymin = -Inf, ymax = Inf, fill = group), 
        inherit.aes = FALSE, alpha = 0.15
    ) +   
    geom_col(colour = "white") + 
    geom_vline(
        data = medians, 
        aes(xintercept = nd_median, group = group), 
        colour = "black", size = 0.5, linetype = "dashed") + 
    labs(
        x = "PTHN across languages", 
        y = "Number of trials", 
        title = "Higher-frequency neighbours\n(stimuli translations)\n"
    ) +

@@

@@

```{r}
#| label: fig-coefs-fixed
#| fig-height: 7
#| fig-width: 6.5
#| fig-cap: "Estimated posterior distributions of coefficients in Model 4. A\\) Population-level effects. Distributions indicate the estimated posterior likelihood density of regression coefficients of fixed effects. Credible intervals (*CrI*), represented with increasingly lighter segmentents in the distribution indicate the range of values that contain the true value with 95\\%, 80\\%, and 50\\% probability. Black dots represent the mean of each distribution. B\\) Participant\\-level coefficient variability. The model estimated participant\\-level coefficients to account for the dependency between responses from the same participant. Distributions in this panel indicate the estimated variability across coefficients from different participants, expressed as standard deviations (*SD*). C\\) Correlation between participant\\-level effects. The model allowed participant-level coefficients to co\\-vary. This panel represents the Pearson correlations between each pair of coefficients, expressed as the mean of the posterior distribution of each  estimated correlation."
coefs <- fixef(fit_4) %>% 
    as.data.frame() %>% 
    rownames_to_column("variable") %>% 
    clean_names() %>% 
    mutate(across(estimate:q97_5, ~ifelse(variable=="Intercept", inv_logit_scaled(.), ./4))) %>% 
    group_split(variable) %>% 
    set_names(make_clean_names(map(., "variable"))) %>% 
    map(select, -variable) %>% 
    map(unlist)

@@

# fixed effects
post_draws %>% 
    filter(str_detect(.variable, "b_")) %>% 
    mutate(
        .variable_name = .variable %>% 
            str_remove("b_") %>% 
            factor(levels = names(str_repl), labels = str_repl),
        .value = ifelse(str_detect(.variable, "Intercept"), inv_logit_scaled(.value), .value/4)
    ) %>% 
    arrange(.variable) %>% 
    ggplot() +
    aes(.value, fct_rev(.variable_name)) +
    geom_vline(xintercept = 0) +
    stat_slab(fill = my_colours[1], colour = my_colours[1]) +
    stat_pointinterval() +
    scale_fill_manual(values = my_colours, na.translate = FALSE) +
    scale_x_continuous(labels = function(x) percent(round(x, 1))) +
    labs(
        x = "P(Correct)", 
        y = "Posterior probability density",
        fill = "CrI"
    ) +
    theme(
        legend.position = c(1, 0.25),
        legend.direction = "vertical",
        legend.background = element_rect(fill = "grey95"),
        legend.key = element_rect(fill = "grey95", colour = "grey95"), 
        legend.key.height = unit(0.1, "cm"),
        axis.title.y = element_blank(),
        legend.text = element_text(size = 7),
        axis.text.x = element_text(colour = "black"),
        axis.text.y = element_text(colour = "black", hjust = 1),
        axis.ticks.y = element_blank(),
        panel.grid.major.y = element_line(colour = "grey", size = 0.5)
    ) 
```

```{r}
#| label: coefs-word
empirical_means <- responses %>% 
    group_by(group) %>% 
    summarise(
        successes = sum(correct, na.rm = TRUE),
        n = n(),
        .groups = "drop"
    ) %>% 
    mutate(
        prop = prop_adj(successes, n),
        prop_se = prop_adj_se(successes, n)
    )

empirical_accuracy <- responses %>% 
    mutate(translation = paste0(word_1, " /", ipa_flat_1, "/ - ",  word_2, " /", ipa_flat_2, "/ - ", percent(lv, accuracy = 1))) %>% 
    group_by(group, translation, lv) %>% 
    summarise(
        successes = sum(correct, na.rm = TRUE),
        n = n(),
        .groups = "drop"
    ) %>% 
    rowwise() %>% 
    mutate(
        prop = prop_adj(successes, n),
        prop_se = prop_adj_se(successes, n), 
    )

fixed_intercept <- fixef(fit_4)[1 ,c(1, 3, 4)] %>% 
    inv_logit_scaled()

post_re <- add_epred_draws(nd_re_words, fit_4, ndraws = 50,
                           re_formula = ~ (1 | translation_id)) %>% 
    group_by(translation_id, nd_std, freq_zipf_2_std, lv_std, group) %>% 
    summarise(
        .mean = mean_qi(.epred)[,1], 
        .lower = mean_qi(.epred)[,2],
        .upper = mean_qi(.epred)[,3],
        .groups = "drop"
    ) %>% 
    ungroup() %>% 
    select(-c(group)) %>% 
    left_join(select(stimuli, group, translation, translation_id, lv)) %>% 
    mutate(translation = paste0(translation, " - ", percent(lv, accuracy = 1))) %>% 
    left_join(select(empirical_accuracy, translation, n, prop, prop_se))

post_re %>% 
    ggplot() +
    aes(x = .mean, y = reorder_within(translation, prop, group)) +
    facet_wrap(~group, scales = "free_y") +
    geom_vline(data = empirical_means, aes(xintercept = prop), size = 0.75, colour = "grey") +
    geom_errorbar(aes(xmin = .lower, xmax = .upper), size = 0.5, colour = "grey", width = 0.5) + 
    geom_point(aes(x = .mean), size = 0.5, colour = "grey") + 
    geom_point(aes(x = prop, colour = group), size = 1, shape = 15) +
    labs(
        x = "Percentage of correct responses",
        y = "Item",
        title = "Observed translation accuracy",
        subtitle = "Dots indicate proportions of correct responses, error bars indicate +/-1 SE",
        colour = "Credible Interval (CrI)",
        caption = "Percentages next to items indicate the Levenshtein distance between both translations."
    ) +
    scale_x_continuous(limits = c(0, 1), labels = percent) +
    scale_y_reordered() +
    theme(
        legend.position = "none",
        legend.key = element_rect(fill = NA, colour = NA),
        axis.text.x = element_text(size = 7),
        axis.text.y = element_text(size = 5, hjust = 1),
        axis.ticks = element_blank(),
        axis.title = element_text(size = 10),
        axis.title.y = element_blank(),
        panel.grid.major.x = element_line(size = 0.15, linetype = "dotted", colour = "grey"),
        plot.caption.position = "plot",
        plot.caption = element_text(size = 9, hjust = 0, face = "plain", margin = margin(t = unit(3, "cm"))),
        plot.title.position = "plot",
        plot.title = element_text(hjust = 0, size = 13),
        plot.subtitle = element_text(hjust = 0, face = "plain", size = 13)
    )

ggsave(here("img", "accuracy.png"), height = 9, width = 10, dpi = 1000)
```

@@

nd <- expand.grid(
    lv_std = seq(
        min(fit_4$data$lv_std, na.rm = TRUE),
        max(fit_4$data$lv_std, na.rm = TRUE),
        by = 0.1
    ),
    freq_zipf_2_std = 0,
    nd_std = scale_values(c(0, 3, 6, 10, 15, 25), fit_4$data$nd)
)

m <- add_epred_draws(nd, fit_4, re_formula = NA, ndraws = 50) %>% 
    mutate(nd_lab = rescale_values(nd_std, fit_4$data$nd) %>% 
               paste0(" neighbours") %>% 
               factor(levels = paste0(c(0, 3, 6, 10, 15, 25), " neighbours"))
    )

ggplot(m, aes(x = lv_std, y = .epred)) +
    facet_wrap(~nd_lab, nrow = 1) +
    geom_line(aes(group = interaction(nd_std, .draw)),
              colour = "grey", size = 0.75, alpha = 0.25) +
    geom_hline(yintercept = 0.5, colour = "grey", size = 1) +
    stat_summary(fun = mean, geom = "line", size = 1, colour = my_colours[2]) +
    labs(
        x = "Phonological similarity (Levenshtein)",
        y = "P(Correct)",
        title = "Population-level posterior predictions"
    ) +
    scale_y_continuous(labels = percent) +
    theme(
        legend.position = "none",
        axis.text.x = element_text(size = 10),
        plot.title = element_blank()
    )
```

@@

```{r}
#| label: tbl-questionnaire-model-coefs
#| warning: false
coefs <- fixef(questionnaire_fit_4) %>% 
    as.data.frame() %>% 
    rownames_to_column("variable") %>% 
    clean_names() %>% 
    mutate(across(estimate:q97_5, ~ifelse(variable=="Intercept", inv_logit_scaled(.), ./4)))

@@

@@

post_draws <-  gather_draws(questionnaire_fit_4, `b_.*`, `sd_.*`, regex = TRUE)

# fixed effects
post_draws %>% 
    filter(str_detect(.variable, "b_")) %>% 
    mutate(
        .variable_name = .variable %>% 
            str_remove("b_") %>% 
            factor(levels = names(str_repl), labels = str_repl),
        .value = ifelse(str_detect(.variable, "Intercept"), inv_logit_scaled(.value), .value/4)
    ) %>% 
    arrange(.variable) %>% 
    ggplot() +
    aes(.value, fct_rev(.variable_name)) +
    geom_vline(xintercept = 0, size = 1, colour = "grey") +
    stat_slab(fill = my_colours[1], colour = my_colours[1]) +
    stat_pointinterval() +
    labs(
        x = "P(Correct)", 
        y = "Posterior probability density",
        fill = "CrI"
    ) +
    scale_x_continuous(labels = function(x) percent(round(x, 1)), breaks = seq(-0.1, 0.5, 0.1)) +
    theme(
        axis.title.y = element_blank(),
        axis.text = element_text(colour = "black", hjust = 1, size = 12),
        axis.line = element_line(size = 0.75),
        panel.grid.major.x = element_line(colour = "grey", linetype = "dotted"),
        axis.ticks.y = element_blank(),
        panel.background = element_blank(),
        panel.border = element_blank()

@@

```{r}
#| label: questionnaire-marginal-effects
#| fig-width: 7
#| fig-height: 3.5
#| fig-cap: "Expected mean posterior predictions from Model 4. A) Population-level predictions: the X-axis and the Y-axis represent the PTHN score (in standard deviations from the mean) and the probability of correct translation, respectively. We simulated 300 observations from the posterior distribution of the model: 100 simulations for translations with no similarity (0% Levenshtein), 100 simulations for translations with mean accuracy (20.51% Levenshtein), and 100 simulations for translations with the maximum observed accuracy (83.33% Levenshtein). We did this across the range of values of the PTHN scores. For each simulation, we drew a single sample from the posterior distribution of each coefficient. Each simulation is depicted in the graph as a line: pink for minimum similarity translations, blue for hight similarity translations, and yellow for maximum similarity translations. Black, thick lines indicate the expected mean value of the posterior predictions of the model for each condition. The dispersion of the lines indicates the uncertainty of our predictions. We computed these posterior predictions for each group of participants, and plot tem in separate panels."
questionnaire_nd <- expand.grid(
    lv_std = seq(
        min(questionnaire_fit_4$data$lv_std, na.rm = TRUE),
        max(questionnaire_fit_4$data$lv_std, na.rm = TRUE),
        by = 0.1
    ),
    freq_zipf_2_std = 0,
    nd_std = scale_values(c(0, 3, 6, 10, 15, 25), questionnaire_fit_4$data$nd)
)

questionnaire_m <- add_epred_draws(nd, questionnaire_fit_4, re_formula = NA, ndraws = 50) %>% 
    mutate(nd_lab = rescale_values(nd_std, questionnaire_fit_4$data$nd) %>% 
               paste0(" neighbours") %>% 
               factor(levels = paste0(c(0, 3, 6, 10, 15, 25), " neighbours"))
    )

ggplot(questionnaire_m, aes(x = lv_std, y = .epred)) +
    facet_wrap(~nd_lab, nrow = 1) +
    geom_line(aes(group = interaction(nd_std, .draw)),
              colour = "grey", size = 0.75, alpha = 0.25) +
    geom_hline(yintercept = 0.5, colour = "grey", size = 1) +
    stat_summary(fun = mean, geom = "line", size = 1, colour = my_colours[2]) +
    labs(
        x = "Phonological similarity (Levenshtein)",
        y = "P(Correct)",
        title = "Population-level posterior predictions"
    ) +
    scale_y_continuous(labels = percent) +
    theme(
        legend.position = "none",
        axis.text.x = element_text(size = 10),
        plot.title = element_blank()
    )
```

@@

```{r}
#| label: fig-joint-marginal-effects
#| fig-width: 9
#| fig-height: 4
#| fig-cap: "Expected mean posterior predictions from Model 4. A) Population-level predictions: the X-axis and the Y-axis represent the PTHN score (in standard deviations from the mean) and the probability of correct translation, respectively. We simulated 300 observations from the posterior distribution of the model: 100 simulations for translations with no similarity (0% Levenshtein), 100 simulations for translations with mean accuracy (20.51% Levenshtein), and 100 simulations for translations with the maximum observed accuracy (83.33% Levenshtein). We did this across the range of values of the PTHN scores. For each simulation, we drew a single sample from the posterior distribution of each coefficient. Each simulation is depicted in the graph as a line: pink for minimum similarity translations, blue for hight similarity translations, and yellow for maximum similarity translations. Black, thick lines indicate the expected mean value of the posterior predictions of the model for each condition. The dispersion of the lines indicates the uncertainty of our predictions. We computed these posterior predictions for each group of participants, and plot tem in separate panels."

>>>>

---
title: "Translation Elicitation: laboratory notes"
date: "Last updated: `r format(Sys.Date(), '%d/%m/%Y')`"
format:
    html:
        toc: true
        number-sections: true
        bibliography: "references.bib"
        csl: "apa7.csl"
        warnings: false
        messages: false
        fig-dpi: 600
        out-width: "80%"
        code-fold: true
        code-tools: true
        code-line-numbers: true
        code-link: true
---

```{r}
#| label: setup
#| include: false
set.seed(888)

my_colours <- c("#1A85FF", "#ff2976", "#FFC20A")

@@

```{r}
#| label: tbl-stimuli
#| tbl-cap: "Lexical frequency, phonological neigbourhood size, and levenshtein distance of the stimuli words."
#| tbl-subcap: "Median and standard deviation (*SD*) of lexical frequencies of target words (expressed in counts per million and as Zipf scores), density of higher-frequency phonological neighbourhoods of target words, and normalised Levenshtein phonological similarity between the presented and the target words."
stimuli %>% 
    select(group, word_1, freq_2, freq_zipf_2, nd, lv) %>% 
    group_by(group) %>% 
    summarise(
        across(
            freq_2:lv, 
            list(
                median = ~median(., na.rm = TRUE),
                sd = ~sd(., na.rm = TRUE)
            )
        )
    ) %>%
    gt(rowname_col = "group") %>% 
    fmt_number(freq_2_median:nd_sd) %>%
    fmt_percent(matches("lv|global")) %>% 
    tab_spanner(
        md("**Freq. (million)**"),
        c("freq_2_median", "freq_2_sd", "freq_zipf_2_median", "freq_zipf_2_sd")
    ) %>% 
    tab_spanner(md("**Freq. (Zipf)**"), matches("freq_zipf_2")) %>% 
    tab_spanner(md("**Neighbours**"), matches("nd")) %>% 
    tab_spanner(md("**Levenshtein**"), matches("lv")) %>% 
    cols_label(
        freq_2_median = md("Median"),
        freq_2_sd = md("*SD*"),
        freq_zipf_2_median = md("Median"),
        freq_zipf_2_sd = md("*SD*"),
        nd_median = md("Median"),
        nd_sd = md("*SD*"),
        lv_median = md("Median"),
        lv_sd = md("*SD*")
    ) %>% 
    summary_rows(
        columns = c(matches("median"), -matches("lv")),
        fns = list(Median = "median", SD = "sd")
    ) %>% 
    summary_rows(
        columns = matches("lv"),
        fns = list(Median = "median", SD = "sd"), 
        formatter = fmt_percent
    ) %>% 
    tab_style(
        style = cell_text(align = "left", weight = "bold", size = "medium"),
        locations = cells_title(groups = "title")
    ) %>% 
    tab_style(
        style = cell_text(align = "left", size = "medium", style = "italic"),
        locations = cells_title(groups = "subtitle")
    ) %>% 
    tab_style(
        style = cell_text(align = "left", size = "medium"),
        locations = cells_source_notes()
    ) %>% 
    tab_style(
        style = cell_text(align = "left", size = "medium"),
        locations = cells_stub_grand_summary()
    ) %>% 
    tab_style(
        style = cell_borders(sides = c("left", "right"), color = "white"),
        locations = list(
            cells_body(),
            cells_row_groups(),
            cells_column_spanners(), 
            cells_stub(),
            cells_stub_grand_summary(), 
            cells_source_notes(),
            cells_column_labels(),
            cells_stubhead()
        )
    ) %>% 
    tab_style(
        style = list(
            cell_text(align = "left", size = "medium"),
            cell_borders(sides = "all", color = "white")
        ),
        locations = cells_stub()
    ) %>% 
    tab_style(
        style = cell_text(
            align = "center", 
            size = "medium",
            weight = "normal",
            style = "normal"
        ),
        locations = list(
            cells_column_spanners(),
            cells_column_labels()
        )
    ) %>% 
    tab_style(
        style = cell_borders(sides = "all", color = "white"),
        locations = cells_body(columns = 1:9)
    ) %>% 
    tab_style(
        style = cell_borders(sides = "top", color = "white"),
        locations = cells_body(columns = 1:9)
    )
```

@@

```{r}
#| label: fig-stimuli-pthn
#| fig-height: 10
stimuli %>% 
    left_join(count(., group, name = "n_total")) %>% 
    mutate(
        translation = paste0(word_1, "/", word_2),
        group = paste0(group,  " (N = ", n_total, ")")
    ) %>% 
    ggplot(aes(x = nd, y = reorder(translation, nd), colour = group, fill = group, label = translation)) +
    facet_wrap(~group, scales = "free_y") +
    geom_segment(aes(x = 0, xend = nd, y = reorder(translation, nd), yend = reorder(translation, nd))) +
    geom_point(size = 1) +
    labs(
        x = "# phonological neighbours", 
        y = "Word"
    ) +
    scale_x_continuous(breaks = seq(0, 30, 5)) +
    theme(
        legend.position = "none",
        panel.grid.major.x = element_line(colour = "grey", linetype = "dotted"),
        axis.ticks.y = element_blank(),
        axis.title.y = element_blank(),
        axis.text.y = element_text(size = 7, hjust = 1)
    )
```

@@

```{r}
#| label: fig-stimuli-lv
#| fig-width: 9
#| fig-height: 12
stimuli %>% 
    left_join(count(., group, name = "n_total")) %>% 
    mutate(
        group = paste0(group,  " (N = ", n_total, ")"),
        translation = paste(translation, "(", percent(lv, accuracy = 0.01), ")"),
        translation_ord = reorder_within(translation, lv, group)
    ) %>% 
    ggplot() +
    aes(x = lv, y = translation_ord, fill = group, colour = group) +
    facet_wrap(~group, scales = "free_y") +
    geom_segment(aes(x = 0, xend = lv, y = translation_ord, yend = translation_ord)) +
    geom_point(size = 1) +
    labs(
        x = "Group", 
        y = "Phonological Leveshtein distance\n(corrected for string length)",
        fill = "Test language"
    ) +
    scale_x_continuous(labels = percent) +
    scale_y_reordered() +
    theme(
        legend.position = "none",
        axis.title.y = element_blank(),
        axis.text.y = element_text(size = 3, hjust = 1),
        panel.grid.major.x = element_line(colour = "grey", linetype = "dotted")
    ) 
ggsave(here("img", "lv.png"), height = 12)
```

@@

    # PTHN 1
    stimuli %>% 
    count(group, nd) %>% 
    ggplot(aes(x = nd, y = n, fill = group)) + 
    facet_wrap(~group, ncol = 1) + 
    geom_rect(
        data = medians, 
        aes(xmin = 0, xmax = nd_median+nd_sd, ymin = -Inf, ymax = Inf, fill = group), 
        inherit.aes = FALSE, alpha = 0.15
    ) +   
    geom_col(colour = "white") + 
    geom_vline(
        data = medians, 
        aes(xintercept = nd_median, group = group), 
        colour = "black", size = 0.5, linetype = "dashed") + 
    labs(
        x = "PTHN across languages", 
        y = "Number of trials", 
        title = "Cross-language neighbours"
    ) +

@@

```{r}
#| label: model-rocs
model_rocs %>% 
    bind_rows(.id = "model") %>% 
    ggplot(aes(1-specificity, sensitivity, colour = model)) +
    facet_wrap(~model) +
    geom_line(aes(group = .draw), alpha = 0.1) +
    labs(x = "1 - Specificity", y = "Sensitivity", colour = "Model") + 
    scale_y_continuous(labels = percent) +
    scale_x_continuous(labels = percent) +
    theme_custom()

@@

```{r}
#| label: fig-coefs-fixed
#| fig-height: 7
#| fig-width: 6.5
#| fig-cap: "Estimated posterior distributions of coefficients in Model 4. A\\) Population-level effects. Distributions indicate the estimated posterior likelihood density of regression coefficients of fixed effects. Credible intervals (*CrI*), represented with increasingly lighter segmentents in the distribution indicate the range of values that contain the true value with 95\\%, 80\\%, and 50\\% probability. Black dots represent the mean of each distribution. B\\) Participant\\-level coefficient variability. The model estimated participant\\-level coefficients to account for the dependency between responses from the same participant. Distributions in this panel indicate the estimated variability across coefficients from different participants, expressed as standard deviations (*SD*). C\\) Correlation between participant\\-level effects. The model allowed participant-level coefficients to co\\-vary. This panel represents the Pearson correlations between each pair of coefficients, expressed as the mean of the posterior distribution of each  estimated correlation."
coefs <- fixef(fit_4) %>% 
    as.data.frame() %>% 
    rownames_to_column("variable") %>% 
    clean_names() %>% 
    mutate(across(estimate:q97_5, ~logit_to_prob(., variable))) %>%
    group_split(variable) %>% 
    set_names(make_clean_names(map(., "variable"))) %>% 
    map(select, -variable) %>% 
    map(unlist)

@@

# fixed effects
post_draws %>% 
    filter(str_detect(.variable, "b_")) %>% 
    mutate(
        .variable_name = factor(
            gsub("b_", "", .variable),
            levels = names(str_repl),
            labels = str_repl
        ),
        .value = logit_to_prob(.value, .variable)
    ) %>% 
    arrange(.variable) %>% 
    ggplot() +
    aes(.value, fct_rev(.variable_name)) +
    geom_vline(xintercept = 0) +
    stat_slab(fill = my_colours[1], colour = my_colours[1]) +
    stat_pointinterval() +
    scale_fill_manual(values = my_colours, na.translate = FALSE) +
    scale_x_continuous(labels = function(x) percent(round(x, 1))) +
    labs(
        x = "P(Correct)", 
        y = "Posterior probability density",
        fill = "CrI"
    ) +
    theme(
        legend.position = c(1, 0.25),
        legend.direction = "vertical",
        legend.background = element_rect(fill = "grey95"),
        legend.key = element_rect(fill = "grey95", colour = "grey95"), 
        legend.key.height = unit(0.1, "cm"),
        axis.title.y = element_blank(),
        legend.text = element_text(size = 7),
        axis.text.x = element_text(colour = "black"),
        axis.text.y = element_text(colour = "black", hjust = 1),
        axis.ticks.y = element_blank(),
        panel.grid.major.y = element_line(colour = "grey", size = 0.5)
    ) 
```

@@

nd <- expand.grid(
    lv_std = seq(
        min(fit_4$data$lv_std, na.rm = TRUE),
        max(fit_4$data$lv_std, na.rm = TRUE),
        by = 0.1
    ),
    freq_zipf_2_std = 0,
    nd_std = scale_values(c(0, 3, 6), fit_4$data$nd)
)

m <- add_epred_draws(nd, fit_4, re_formula = NA, ndraws = 50) %>% 
    mutate(
        nd_lab = rescale_values(nd_std, fit_4$data$nd) %>% 
            paste0(" neighbours") %>% 
            factor(levels = paste0(c(0, 3, 6), " neighbours"))
    )

ggplot(m, aes(x = lv_std, y = .epred)) +
    facet_wrap(~nd_lab, nrow = 1) +
    geom_line(aes(group = interaction(nd_std, .draw)),
              colour = my_colours[1], size = 0.75, alpha = 0.1) +
    geom_hline(yintercept = 0.5, colour = "grey", size = 1) +
    stat_summary(fun = mean, geom = "line", size = 1, colour = my_colours[1]) +
    labs(
        x = "Phonological similarity (Levenshtein)",
        y = "P(Correct)",
        title = "Population-level posterior predictions"
    ) +
    scale_y_continuous(labels = percent) +
    theme(
        legend.position = "none",
        axis.text.x = element_text(size = 10),
        plot.title = element_blank()
    )
```

@@

```{r}
#| label: tbl-questionnaire-model-coefs
#| warning: false
questionnaire_coefs <- fixef(questionnaire_fit_4) %>% 
    as.data.frame() %>% 
    rownames_to_column("variable") %>% 
    clean_names() %>% 
    mutate(across(estimate:q97_5, ~ifelse(variable=="Intercept", plogis(.), ./4)))

@@

questionnaire_coefs %>% 
    mutate(
        variable = variable %>% 
            str_remove("b_") %>% 
            factor(levels = names(str_repl), labels = str_repl)
    ) %>% 
    select(-est_error) %>% 
    gt() %>% 
    fmt_percent(2:4) %>% 
    cols_merge(c("q2_5", "q97_5"), pattern = "[{1}, {2}]") %>% 
    cols_label(
        variable = md("**Predictor**"),
        estimate = md("**Mean**"),
        q2_5 = md("**95\\% CrI**"),
    ) %>% 
    tab_source_note(tab_caption) %>% 
    cols_align(align = "left")
```

@@

questionnaire_post_draws <- gather_draws(questionnaire_fit_4, `b_.*`, `sd_.*`, regex = TRUE)

# fixed effects
questionnaire_post_draws %>% 
    filter(str_detect(.variable, "b_")) %>% 
    mutate(
        .variable_name = .variable %>% 
            str_remove("b_") %>% 
            factor(levels = names(str_repl), labels = str_repl),
        .value = ifelse(str_detect(.variable, "Intercept"), inv_logit_scaled(.value), .value/4)
    ) %>% 
    arrange(.variable) %>% 
    ggplot() +
    aes(.value, fct_rev(.variable_name)) +
    geom_vline(xintercept = 0, size = 1, colour = "grey") +
    stat_slab(fill = my_colours[1], colour = my_colours[1]) +
    stat_pointinterval() +
    labs(
        x = "P(Correct)", 
        y = "Posterior probability density",
        fill = "CrI"
    ) +
    scale_x_continuous(labels = function(x) percent(round(x, 1)), breaks = seq(-0.1, 0.5, 0.1)) +
    theme(
        axis.title.y = element_blank(),
        axis.text = element_text(colour = "black", hjust = 1, size = 12),
        axis.line = element_line(size = 0.75),
        panel.grid.major.x = element_line(colour = "grey", linetype = "dotted"),
        axis.ticks.y = element_blank(),
        panel.background = element_blank(),
        panel.border = element_blank()

@@

```{r}
#| label: questionnaire-marginal-effects
#| fig-width: 7
#| fig-height: 3.5
#| fig-cap: "Expected mean posterior predictions from Model 4. A) Population-level predictions: the X-axis and the Y-axis represent the PTHN score (in standard deviations from the mean) and the probability of correct translation, respectively. We simulated 300 observations from the posterior distribution of the model: 100 simulations for translations with no similarity (0% Levenshtein), 100 simulations for translations with mean accuracy (20.51% Levenshtein), and 100 simulations for translations with the maximum observed accuracy (83.33% Levenshtein). We did this across the range of values of the PTHN scores. For each simulation, we drew a single sample from the posterior distribution of each coefficient. Each simulation is depicted in the graph as a line: pink for minimum similarity translations, blue for hight similarity translations, and yellow for maximum similarity translations. Black, thick lines indicate the expected mean value of the posterior predictions of the model for each condition. The dispersion of the lines indicates the uncertainty of our predictions. We computed these posterior predictions for each group of participants, and plot tem in separate panels."
questionnaire_nd <- expand.grid(
    lv_std = seq(
        min(questionnaire_fit_4$data$lv_std, na.rm = TRUE),
        max(questionnaire_fit_4$data$lv_std, na.rm = TRUE),
        by = 0.1
    ),
    freq_zipf_2_std = 0,
    nd_std = scale_values(c(0, 3, 6), questionnaire_fit_4$data$nd)
)

questionnaire_m <- add_epred_draws(
    questionnaire_nd,
    questionnaire_fit_4, 
    re_formula = NA,
    ndraws = 50
) %>% 
    mutate(
        nd_lab = rescale_values(nd_std, questionnaire_fit_4$data$nd) %>% 
            round(2) %>% 
            paste0(" neighbours") %>% 
            factor(levels = paste0(c(0, 3, 6), " neighbours"))
    )

ggplot(questionnaire_m, aes(x = lv_std, y = .epred)) +
    facet_wrap(~nd_lab, nrow = 1) +
    geom_line(aes(group = interaction(nd_std, .draw)),
              colour = my_colours[2], size = 0.75, alpha = 0.1) +
    geom_hline(yintercept = 0.5, colour = "grey", size = 1) +
    stat_summary(fun = mean, geom = "line", size = 1, colour = my_colours[2]) +
    labs(
        x = "Phonological similarity (Levenshtein)",
        y = "P(Correct)",
        title = "Population-level posterior predictions"
    ) +
    scale_y_continuous(labels = percent) +
    theme(
        legend.position = "none",
        axis.text.x = element_text(size = 10),
        plot.title = element_blank()
    )
```

@@

## Regression coefficients
